---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/liao961120/linguisticsdown.svg?branch=master)](https://travis-ci.org/liao961120/linguisticsdown)
[![Support R Version](https://img.shields.io/badge/R-≥%203.4.0-blue.svg)](https://cran.r-project.org/)

# linguisticsdown

The goal of linguisticsdown is to support Linguistics-related doucument writing in R Markdown, such as providing a [Shiny Gadget](https://shiny.rstudio.com/articles/gadgets.html) to write and insert IPA symbols easily and functions to draw syntax tree (not implemented yet).

## Installation
```{r}
devtools::install_github("liao961120/linguisticsdown")
```


## Example

Launch shiny gadget for inserting IPA symbols:
```{r example}
library(linguisticsdown)
writeIPA()
```

Lookup IPA symbols' phonetic features and X-SAMPA input:
```{r}
searchIPA()
```


## To Do

1. Draw Syntax Tree

